A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-30 doc/paper1-submission/paper5-adjusted.tex
Unify Fig13
Remove funding statements.
Show monotypic taxa in panel 5c.

\caption{Exemplified input trees (a-b) and taxonomy tree (c) from Fig. \ref{fig:cleaned-phylo-example}.
Taxon E in (a) is exemplified by E1. Pruned taxa are E2, F2, and D. The
taxa E and F are retained as monotypic taxa in the pruned taxonomy
$\protect\prunedTaxonomy$, but are not shown in panel (c). The red
edge in the pruned taxonomy tree is an uncontested higher taxon in
the exemplified taxonomy (as explained in section \ref{subsec:Subproblem-decomposition})}
\label{fig:exemplify-example}
\end{figure}

@@

\caption{Subproblems \emph{ABCD} and \emph{root} generated from the exemplified trees shown in Fig. \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.
Similarly, the trivial problems that list E1 and F1 as the only daughters
of taxa E and F have been omitted.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig7}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig9}

@@

\begin{figure}
\includegraphics[width=1.0\textwidth]{Fig12}

\caption{\label{fig:Two-approaches-to-unpruning}Two approaches to unpruning.
Taxa G and R in the taxonomy (a) are broken because they conflict
with the grafted solution (b). Removing these broken taxa from the
taxonomy before unpruning leads to taxa R4, R5, and R6 being attached
directly at taxon N, as in tree (c). In tree (d), the children of
the broken taxon R are instead attached at the MRCA of R1, R2, and
R3. Our method follows the second approach.}
\end{figure}

>>>>

\caption{Exemplified input trees (a-b) and taxonomy tree (c) from Fig. \ref{fig:cleaned-phylo-example}.
Taxon E in (a) is exemplified by E1. Pruned taxa are E2, F2, and D. The
taxa E and F are retained as monotypic taxa in the pruned taxonomy
$\protect\prunedTaxonomy$. The red
edge in the pruned taxonomy tree is an uncontested higher taxon in
the exemplified taxonomy (as explained in section \ref{subsec:Subproblem-decomposition})}
\label{fig:exemplify-example}
\end{figure}

@@

\caption{Subproblems \emph{ABCD} and \emph{root} generated from the exemplified trees shown in Fig. \ref{fig:exemplify-example}.
A trivial statement from the first tree that a taxon labelled $ABCD$
is sister to $E$ has been omitted, because trees with only 2 leaves
do not contain phylogenetic information.
Similarly, the trivial problems that list E1 and F1 as the only daughters
of taxa E and F have been omitted.}
\label{fig:subproblems-example}
\end{figure}
\begin{figure}
\subfloat[]{\includegraphics[scale=0.57]{Fig7a}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7b}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7c}

\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7d}

}\hfill{}\subfloat[]{\includegraphics[scale=0.57]{Fig7e}

}\hfill{}

@@

\begin{figure}
\hfill{}\subfloat[Solution to subproblem \emph{ABCD}]{\includegraphics[scale=0.55]{Fig9a}

}\hfill{}\subfloat[Solution to subproblem \emph{root}]{\includegraphics[scale=0.55]{Fig9b}

}\hfill{}

@@

\begin{figure}
\begin{centering}
\subfloat[Taxonomy]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.38]{Fig12a}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}\subfloat[Grafted solution]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.38]{Fig12b}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}
\par\end{centering}
\begin{centering}
\subfloat[Unpruned tree - broken taxa removed]{\begin{centering}
\includegraphics[scale=0.38]{Fig12c}
\par\end{centering}
}\hfill{}\subfloat[Unpruned tree with MRCA-attachment]{\begin{centering}
\includegraphics[scale=0.38]{Fig12d}
\par\end{centering}
}
\par\end{centering}
\caption{\label{fig:Two-approaches-to-unpruning}Two approaches to unpruning.
Taxa G and R in the taxonomy (a) are broken because they conflict
with the grafted solution (b). Removing these broken taxa from the
taxonomy before unpruning leads to taxa R4, R5, and R6 being attached
directly at taxon N, as in tree (c). In tree (d), the children of
the broken taxon R are instead attached at the MRCA of R1, R2, and
R3. Our method follows the second approach.}
\end{figure}
